Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-02-11 Manuscript/R&R/01-reviewer_1.Rmd
Update R&R
Add R&R to the target pipeline; start to draft response.

@@

@@

>>>>

__Response__: Thank you for the comment. We expanded our simulation study from two perspectives: 1) we added linear lasso models and spikeSlabGAM models, where linear lasso models serve as the reference to benchmark the performance of linear models; 2) we added new scenarios where the the functional form of each predictors are linear, to demonstrate the robustness of the proposed, regarding prediction and variable selection performances, when the non-linear assumption no longer holds. Please see the changes and conclusion in \emph{Section 3: SIMULATION STUDY}. To conclude, we observed [TODO: REPLACE HERE WITH CONCLUSION]. Hence, the proposed models perform better than linear models when functional are non-linear and as good as linear model when functions are linear. The expanded simulation study also demonstrates that the proposed model is flexible to model both linear and non-linear effects and broadly applicable in high-dimensional modeling without much constraints, which deems to be an additional strength.

@@

__Response__:
\bigskip

@@

__Response__:
